taxadb: A High-Performance Local Taxonomic Database Interface

### 2019-01-09 paper/manuscript.Rmd
fuzzy name matching, name cleaning (WIP)

```{r}
bbs_ids <- bbs %>% 
  select(species) %>% 
  mutate(species = clean_names(species)) %>%
  mutate(gbif = get_ids(species, "gbif", "prefix"),
          col = get_ids(species, "col", "prefix"),
         itis = get_ids(species, "itis", "prefix"),
         ncbi = get_ids(species, "ncbi", "prefix"),
     wikidata = get_ids(species, "wd", "prefix"),
          ott = get_ids(species, "ott","prefix") 
  )

bbs_ids %>% 
  select(-species) %>% 
  purrr::map_dbl(function(x) sum(!is.na(x)))
```

>>>>

`get_ids` by default looks only for exact matches.  We can get more matches by cleaning the names first.  `clean_names()`

```{r}
clean_names(bbs$species, 
            )
```
